Supplement to: Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-05-19 synthesizerOutputs.tex
latest synthesis results in the supplement

@@

@@

@@

@@

>>>>

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
rectangle(-6*i + 12,2*i + 3,-6*i + 14,9);
rectangle(-6*i + 15,5*i + -2,-6*i + 17,9)
}
line(12,9,12,0,
arrow = True,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(1,5);
for (i < 3){
if (i > 0){
line(-4*i + 12,1,-4*i + 10,1,
arrow = True,solid = True);
rectangle(-4*i + 12,4,-4*i + 14,6)
}
line(-4*i + 9,2,-4*i + 9,4,
arrow = True,solid = True);
rectangle(-4*i + 8,0,-4*i + 10,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
for (j < 3){
if (j > 0){
line(-3*j + 8,-3*i + 7,-3*j + 9,-3*i + 7,
arrow = False,solid = True);
line(-3*i + 7,-3*j + 8,-3*i + 7,-3*j + 9,
arrow = False,solid = True)
}
circle(-3*j + 7,-3*i + 7)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(0,0,6,2);
reflect(reflect(x = 6)){
rectangle(0,3,2,9);
for (i < 3){
circle(5,2*i + 4);
circle(2*i + 1,1)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(3,1);
reflect(reflect(x = 6)){
for (i < 3){
if (i > 0){
circle(1,-4*i + 13);
line(5,-4*i + 12,-2*i + 7,-4*i + 10,
arrow = True,solid = True)
}
line(1,8,4,5,
arrow = True,solid = True)
}
}
        \end{verbatim}
\end{minipage}
